Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-12 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{Distributed Decision Making Model for Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals. Moreover, these solutions generally suffer from high computational complexity, which makes decision making impossible in an real-time fashion. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Utilizing the training model, the decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that using this data, communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using using real data from 142 users on 4,532 web services over 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
